Figures

### 2025-03-19 notebooks/figures.qmd
draft 3 complete. Also full project render

}

@@

# safety concerns by treatment
safety.concern.treat.likert <- data |>
  # Need to slightly modify text of factor levels
  mutate(across(
    c(q25, q36),
    ~ pewmethods::fct_case_when(
      .x == "Very concerned" ~ "Very concerned",
      .x == "Somewhat concerned" ~ "Somewhat concerned",
      .x %in% c("Not too concerned", "Somewhat unconcerned") ~ "Not too concerned",
      .x == "Not at all concerned" ~ "Not at all concerned",
      TRUE ~ NA
    )
  )) |>
  likert_plot(
    x = c(q25, q36),
    y = 'group',
    facet_rows = vars(.question),
    facet_label_wrap = 15,
    variable_labels = c(q25 = 'Thinking about Maricopa County, AZ', q36 = "Thinking about Local Area"),
    title = "Concern for Voter Intimidation, Threats, or Violence by Treatment Condition",
    subtitle = str_wrap(
      "How concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?",
      width = 99
    )
  )
```

@@

# q26 In-person voter safety at election sites by treatment
safety.conf.treat.likert <- data |>
  likert_plot(
    x = c(q26, q37), 
    y = 'group',
    facet_label_wrap = 15,
    facet_rows = vars(.question),
    variable_labels = c(
      q26 = "In Maricopa County, AZ",
      q37 = "In your local area"
    ),
    title = str_wrap("Confidence for In-person voter safety at Polling Sites by Treatment", width = 95),
    subtitle = str_wrap("How confident, if at all, are you that in person polling places will be safe places for voters to cast their ballots during the upcoming elections in November?", width = 95)
  )

@@

```{r}
#| label: fig-patch15

p15.safety.treat <- safety.concern.treat.likert/safety.conf.treat.likert+
  patchwork::plot_layout(guides = "keep")

@@

>>>>

}
```

```{r}
#| label: custom-barplot

# function for creating barplots
custom_barplot <- function(data, x, group, title = NULL, subtitle = NULL,
                           caption = NULL, legend_fill = NULL,
                           xlab = NULL){
  b <- data |> 
    group_by({{ group }}, {{ x }}) |> 
    count() |> 
    drop_na() |> 
    group_by({{ group }}) |> 
  mutate(prop = round(n/sum(n), digits = 3),
         pct = prop*100,
         res = str_c(pct,'% (', n, ')', sep = "")) |> 
  ggplot(aes(x = {{ x }}, y = pct, fill = {{ group }}))+
  geom_bar(position = 'dodge', stat = 'identity')+
  geom_text(aes(label = res), position = position_dodge(1.0), size = 2.5, vjust = -0.5)+
  scale_fill_grey(start = 0.5, end = 0.1)

  b <- b + ggplot2::labs(
    title = title,
    subtitle = subtitle,
    caption = stringr::str_wrap(caption, width = 99),
    fill = legend_fill,
    y = "Percentage",
    x = stringr::str_wrap(xlab, width = 85))
  b
}

@@

# safety concerns by treatment
safety.concern.treat.likert <- data |>
  # Need to slightly modify text of factor levels
  mutate(across(
    c(q25, q36),
    ~ pewmethods::fct_case_when(
      .x == "Very concerned" ~ "Very concerned",
      .x == "Somewhat concerned" ~ "Somewhat concerned",
      .x %in% c("Not too concerned", "Somewhat unconcerned") ~ "Not too concerned",
      .x == "Not at all concerned" ~ "Not at all concerned",
      TRUE ~ NA
    )
  )) |>
  likert_plot(
    x = c(q25, q36),
    y = 'group',
    facet_rows = vars(.question),
    facet_label_wrap = 15,
    variable_labels = c(q25 = 'Thinking about Maricopa County, AZ', q36 = "Thinking about Local Area"),
    subtitle = str_wrap(
      "How concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?",
      width = 99
    )
  )+
  theme(
    text = element_text(family = 'TeX Gyre Pagella'), 
    axis.title.y.left = element_blank())

@@

# q26 In-person voter safety at election sites by treatment
safety.conf.treat.likert <- data |>
  likert_plot(
    x = c(q26, q37), 
    y = 'group',
    facet_label_wrap = 15,
    facet_rows = vars(.question),
    variable_labels = c(
      q26 = "In Maricopa County, AZ",
      q37 = "In your local area"
    ),
    subtitle = str_wrap("How confident, if at all, are you that in person polling places will be safe places for voters to cast their ballots during the upcoming elections in November?", width = 95)
  )+
  theme(
    text = element_text(family = 'TeX Gyre Pagella'), 
    axis.title.y.left = element_blank())

@@

```{r}
#| label: fig-patch15
#| fig-height: 4.5
#| fig-width: 8

p15.safety.treat <- safety.concern.treat.likert/safety.conf.treat.likert+
  patchwork::plot_layout(guides = "keep")+
  patchwork::plot_annotation(
    title = str_wrap("Safety Concerns by Experiment Condition", width = 80), 
    tag_levels = "a")

p15.safety.treat

An alternative

```{r}
#| label: fig-safety
#| layout-nrow: 2
#| fig-height: 3.5
#| fig-cap: "Safety Concerns by Experiment Condition"
#| fig-subcap: 
#|   - "Confidence for In-person voter safety at Election Sites"
#|   - "Concern for Voter Intimidation, Threats, or Violence"

# safety concerns by treatment
safety.concern.treat.likert <- data |>
  # Need to slightly modify text of factor levels
  mutate(across(
    c(q25, q36),
    ~ pewmethods::fct_case_when(
      .x == "Very concerned" ~ "Very concerned",
      .x == "Somewhat concerned" ~ "Somewhat concerned",
      .x %in% c("Not too concerned", "Somewhat unconcerned") ~ "Not too concerned",
      .x == "Not at all concerned" ~ "Not at all concerned",
      TRUE ~ NA
    )
  )) |>
  likert_plot(
    x = c(q25, q36),
    y = 'group',
    facet_rows = vars(.question),
    facet_label_wrap = 15,
    variable_labels = c(q25 = 'Thinking about Maricopa County, AZ', q36 = "Thinking about Local Area"),
    subtitle = str_wrap(
      "How concerned should voters feel about potential violence, threats of violence, or intimidation while voting in person at their local polling place?",
      width = 99
    )
  )+
  theme(
    text = element_text(family = 'TeX Gyre Pagella'), 
    axis.title.y.left = element_blank())

# In-person voter safety at election sites by treatment
safety.conf.treat.likert <- data |>
  likert_plot(
    x = c(q26, q37), 
    y = 'group',
    facet_label_wrap = 15,
    facet_rows = vars(.question),
    variable_labels = c(
      q26 = "In Maricopa County, AZ",
      q37 = "In your local area"
    ),
    subtitle = str_wrap("How confident, if at all, are you that in person polling places will be safe places for voters to cast their ballots during the upcoming elections in November?", width = 95)
  )+
  theme(
    text = element_text(family = 'TeX Gyre Pagella'), 
    axis.title.y.left = element_blank())

# fig a
safety.concern.treat.likert

# fig b
safety.conf.treat.likert

@@

## Barplots

```{r}
#| label: fig-bars-create
#| eval: true
#| include: false

bar_q25 <- custom_barplot(
    data = data,
    x = q25,
    group = group
  ) +
  coord_cartesian(ylim = c(0,60), expand = T)

bar_q26 <- custom_barplot(
  data = data,
  x = q26,
  group = group
)  +
  coord_cartesian(ylim = c(0,60), expand = T)

bar_q36 <- custom_barplot(
  data = data,
  x = q36,
  group = group
)  +
  coord_cartesian(ylim = c(0,60), expand = T)

bar_q37 <- custom_barplot(
  data = data,
  x = q37,
  group = group 
) +
  coord_cartesian(ylim = c(0,60), expand = T)

```{r}
#| label: fig-bars1
#| layout-ncol: 1
#| layout-nrow: 2
#| fig-cap: "Safety Concerns by Experiment Condition"
#| fig-subcap: 
#|   - "Concern for Violence in Maricopa County, AZ Elections"
#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"

bar_q25
bar_q26

```{r}
#| label: fig-bars2
#| layout-ncol: 1
#| layout-nrow: 2
#| fig-cap: "Safety Concerns by Experiment Condition"
#| fig-subcap: 
#|   - "Concern for Violence in Local Area Elections"
#|   - "Confidence in Voter Saftey at Election Sites in Local Area"

bar_q36
bar_q37

```{r}
#| label: fig-bars-alt
#| layout-nrow: 2
#| fig-cap: "Safety Concerns by Experiment Condition"
#| fig-subcap: 
#|   - "Concern for Violence in Maricopa County, AZ Elections"
#|   - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"

bar_q25 <- custom_barplot(
    data = data,
    x = q25,
    group = group
  ) +
  coord_cartesian(ylim = c(0,60), expand = T)

bar_q26 <- custom_barplot(
  data = data,
  x = q26,
  group = group
)  +
  coord_cartesian(ylim = c(0,60), expand = T)

bar_q36 <- custom_barplot(
  data = data,
  x = q36,
  group = group
)  +
  coord_cartesian(ylim = c(0,60), expand = T)

bar_q37 <- custom_barplot(
  data = data,
  x = q37,
  group = group 
) +
  coord_cartesian(ylim = c(0,60), expand = T)

bars1 <- (bar_q25 + bar_q26)+
  patchwork::plot_layout(guides = "collect") &
  theme(
    text = element_text(family = "TeX Gyre Pagella"),
    legend.position = "bottom", 
    axis.title.y.left = element_blank(), 
    axis.text.y.left = element_blank(), 
    axis.ticks.y = element_blank())

bars2 <- (bar_q36 + bar_q37)+
  patchwork::plot_layout(guides = "collect") &
  theme(
    text = element_text(family = "TeX Gyre Pagella"),
    legend.position = "bottom", 
    axis.title.y.left = element_blank(), 
    axis.text.y.left = element_blank(), 
    axis.ticks.y = element_blank())

bars1
bars2

```{r}
#| label: fig-bars-alt2
#| layout-ncol: 2
#| layout-nrow: 2
#| fig-cap: "Concerns for Safety"
#| fig-subcap:
#|    - "Concern for Violence in Maricopa County, AZ Elections"
#|    - "Confidence in Voter Saftey at Election Sites in Maricopa County, AZ"
#|    - "Concern for Violence in Local Area Elections"
#|    - "Confidence in Voter Saftey at Election Sites in Local Area"

bar_q25 <- custom_barplot(data = data, x = q25, group = group)

bar_q26 <- custom_barplot(data = data, x = q26, group = group)

bar_q36 <- custom_barplot(data = data, x = q36, group = group)

bar_q37 <- custom_barplot(data = data, x = q37, group = group)

bar_q25
bar_q26
bar_q36
bar_q37
